Title

### 2024-05-07 paper/main.tex
Updates

% Packages added by me.
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{todonotes}

@@

@@

Chi-Squared and Cram\'er's V

@@

@@

\subsubsection{Mixed data}
Recently multiple tests for mixed data have been proposed but they do not have
an effect size measure.

\subsection{Canonical Correlations}

\section{Effect size for mixed data}
\subsection{Non-conditional Case}
\subsection{Conditional Case}

@@

@@

This is a possibility that this greedy expert gets stuck at incorrect graph structures as it does not do any backtracking to fix its earlier mistakes.

\subsection{Results}

>>>>

% Packages added by me.
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{todonotes}
\usepackage{bm}
\usepackage{subcaption}

\def\ci{\perp\!\!\!\!\!\perp}

@@

\begin{figure}
		\centering
		\begin{tikzpicture}
			\begin{scope}[yshift=0.7cm, scale=0.8]
			\tikzstyle{every node}=[align=center, inner sep=1pt]
				\node (sex) at (-0.7, -0.8) {Sex};
				\node (age) at (-0.3, 0) {Age};
				\node (ed) at (-1.8, -1.6) {Education};
				\node (occ) at (1.8, 0) {Occupation};
				\node (hrpw) at (1.3, -1.6) {Hours Per \\ Week};
				\node (income) at (-0.7, -2.8) {Income};

				\draw[->]  (age) to[bend right=20] (ed);
				\draw[->]  (sex) to (ed);
				\draw[->]  (age) to (hrpw);
				\draw[->]  (ed) to (hrpw);
				\draw[->]  (sex) to (hrpw);
				\draw[->]  (ed) to (income);
				\draw[->]  (hrpw) to (income);
				\draw[->]  (occ) to[out=300, in=0, looseness=1.4] (income.east);
				\draw[->]  (sex) to (income);
				\draw[->]  (ed) to[out=90, in=150, looseness=1.3] (occ);
				\draw[->]  (sex) to (occ);	
			\end{scope}
			\draw[thick, ->, double, cyan] (2.5,0) -- (3,0);
			\node[rectangle, align=center, inner sep=1pt] at (6, 0) {
				\begin{minipage}{\textwidth}
					\begin{equation*}
						\begin{split}
							\textnormal{Age} &\ci \textnormal{Incm} \rvert \textnormal{Edct, Hrpw, Sex} \\
							\textnormal{Age} &\ci \textnormal{Occp} \rvert \textnormal{Edct, Sex} \\
							\textnormal{Age} &\ci \textnormal{Sex} \\
							\textnormal{Hrpw} &\ci \textnormal{Occp} \rvert \textnormal{Edct, Sex} \\
						\end{split}
					\end{equation*}
				\end{minipage}
				};
		\end{tikzpicture}
		\caption{\todo[inline]{Show a full example of testing using this model}}
\end{figure}

@@

When $ \bm{Z} = \emptyset $, in the case of discrete variables, chi-squared test can be used. Effect size 
measures such as Cram\'er's V are available for it.

When $ \bm{Z} \neq \emptyset $, we do stratification.

@@

When $ \bm{Z} = \emptyset $, ordinal variable can be assumed to be coming from a thresholded normal distribution, estimate the thresholds and latent variable to compute 
the correlation coefficient.

@@

\subsubsection{Mixed data}
Recently multiple tests for mixed data have been proposed but they do not have
an effect size measure. We propose one based on canonical correlations.

\subsection{Canonical Correlations}
Canonical correlations are generalization of correlations to set of variables.

\section{Effect size for mixed data}
\subsection{Non-conditional Case}
\subsection{Conditional Case}
\subsection{Connection to special cases}

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.5\textwidth}
		\includegraphics[scale=0.25]{../../presentations/2024_05_das/1.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\includegraphics[scale=0.25]{../../presentations/2024_05_das/2.png}
	\end{subfigure}
	\caption{\todo[inline]{Insert screenshots of the web-tool}}
\end{figure}

@@

There is a possibility that this greedy expert gets stuck at incorrect graph structures as it does not do any backtracking to fix its earlier mistakes.

\subsection{Results}
\begin{figure}
	\begin{subfigure}{0.5\textwidth}
		\includegraphics{../code/plots/shd_ribbon.pdf}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\includegraphics{../code/plots/sid_ribbon.pdf}
	\end{subfigure}
\end{figure}
